XXX

### 2012-03-24 paper/engNERwiki.tex
Another subsection.

The corpus is based on the Wikipedia snapshot as of XXX. The xml files were parsed with the XXX (Attila) parser. The raw text was tokenized with a modified version of the XXX sentence tokenizer in NLTK (CITE). The words were lemmatized with XXX and POS tagged with HunPos (CITE). Chunking was performed with HunChunk (CITE). Experiments have shown that HunPos obtains STAT f-score on the Brown corpus; HunChunk performs at around STAT, CITE?.

@@

@@

tokenizálás: built in-house, tailored for Hungarian, because of the specialities of Hungarian (e.g. period after years in date expressions)

ocamorph + hundisambig, a lemmatizálás miatt

a KR-ban nincs jelölve a proper noun külön

DBPedia--CoNLL mapping for Hungarian: az angol oldalak vannak megcímkézve --> csak azok a magyar oldalak vannak letöltve és feldolgozva, amik megvannak angolul is
	--> future work: kibővíteni azokkal a magyar cikkekkel is, amik nincsenek angolul

>>>>

The English corpus is based on the Wikipedia snapshot as of XXX. The xml files were parsed with the mwlib (CITE) parser. The raw text was tokenized with a modified version of the XXX sentence tokenizer in NLTK (CITE). The words were lemmatized with XXX and POS tagged with HunPos (CITE). Chunking was performed with HunChunk (CITE). Experiments have shown that HunPos obtains STAT f-score on the Brown corpus; HunChunk performs at around STAT, CITE?.

@@

\subsection{Tools}

While NLTK has excellent tools for English, Hungarian is not supported. Therefore, we worked with the tools developed by the Hungarian computational linguist community. For sentence tokenization we used an in-house statistical chunker tailored for Hungarian. It has been trained on the Szeged corpus and it handles the peculiarities of Hungarian ortography, such as the periods placed after numbers in date expressions. Although HunPos, as its name implies, is fully capable of POS tagging Hungarian text, we opted for Hunmorph (CITE), a morphological analyzer that also XXX lemmatizes the words. Hundisambig (CITE) was used to select the right analysis based on the word context\footnote{Incidentally, Hundisambig relies on HunPos for its HMM model.}.

The Hungarian part-of-speech taggers output KR codes (CITE). In addition to the POS category, the KR code also includes inflection information, such as the number, person and case XXX, which makes it much better suited to agglutinative languages than Penn Treebank POS tags. One shortcoming of the KR code is that it does not differenciate between common and proper nouns. Since in Hungarian only proper nouns are capitalized, we can usually decide whether a noun is proper or not based on its ortography. However, this rule cannot be used if the noun is at the beginning of a sentence, as words at the beginning of sentences are always capitalized. Hence, all sentences that begin with nouns have been removed from the corpus.

@@
